Reliable error estimation for Sobol' indices

### 2016-03-10 article.tex
Updating all changes so far. Includes both articles as article.tex and replicated_sobol.tex

@@

\section{Reliable Error Estimation for Cubatures}

\section{Sobol' Sequences and Permuted Points}

>>>>

\section{Estimators---> Correlation 2 Oracle 2}
\subsection{Choice and parameters (threshold small)}
\subsection{Cost discussion ---> Consider or not total order}
Cost small:\[n(d+1)+d_sn+n\]
Cost pas small:\[\alpha n d_s +n+(d-d_s)n\]
Cost small - cost pas small: \[n\sum_{i=1}^{s}(2-\alpha_i+1)\] $s$ number of small indices, $alhpa_i$ proportion of how many more points if not pas small

@@

\section{Reliable Error Estimation for Cubatures}
\subsection{Definition of $\widehat{S}$ (fix it with max and min)}

\section{Sobol' Sequences and Permuted Points}
7 digits $L$ bi/tri diagonal but $L'$ identity up 7 digits.
Fix $L_j$ for each dimension differently?
If we fix the initial number of digits to 7, we have $7!$ different permutations of the points or Owen scramblings which means that if we take $d$ such that $2d>7!$, some dimensions will share the same points. Therefore, we need to scramble each dimension differently ($L'$).
